Theories of deliberated choice

### 2024-05-20 simple.tex
Defs indicative (truly, newly)

While $I$ and $\allargs$ are fundamental sets whose elements are considered elementary, a few notations and concepts are required to define ${\allleadsto}$.
Throughout the article, $\N$ includes zero and $\N^* = \N \setminus \set{0}$.
Given $j, l \in \N$, the notation $\intvl{j, l}$ represents $\set{k \in \N \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \N^*: \intvl{j, 0} = \emptyset$).
Define $\allhists = \bigcup_{k \in \N} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
A generic element of $\allhists$ (a possibly empty finite sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path. Its length is denoted by $\card{\hist} \in \N$ and its elements, $\hist(k)$ or $\hist_k$.
Thus, given an argumentative path $\hist \in \allhists$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$. A path $\hist$ is a sub-path of another path $\histp$ whenever $\hist \subseteq \histp$, thus, $\forall k \in \intvl{1, \card{\hist}}: \hist_k = \histp_k$.

@@

\subsection{An example and a discussion about observability}
The following toy example is inspired by an argument from \citet[p.~59]{railton_facts_2003}. Here is his argument.
\begin{quote}
  An experiment in cognitive psychology reveals that when subjects observe two individuals taking a test, one of whom answers a high percentage of the early questions correctly but then falters, while the other does
  poorly initially but then answers a high percentage of the later questions
  correctly, the first is usually viewed as more able, even though in the end
  each answers the same number of questions correctly in all. If the subjects had been asked which test-taker they would prefer as a math tutor,
  they likely would have answered “The first,” and perhaps they would also
  have been willing to pay a premium to secure his services. But if they
  were to become convinced of the influence of sheer order on their evaluations of relative ability, they presumably would no longer want their
  initial preference for the first test-taker to influence their choices – or
  willingness to pay – in this way.
\end{quote}
\begin{example}[Math tutor]
  \label{ex:tutor}
  Let $I$ be a set of individuals desiring to evaluate two candidates $\set{m_1, m_2}$ for math tutoring.
  Consider one individual $i \in I$.
  Let ${\allleadsto}(i, a_1)$ represent $i$ being shown a test of candidate $m_1$ wherein $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly.
  Let ${\allleadsto}(i, a_2)$ represent $i$ being shown a test of candidate $m_2$ wherein $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
  %	Let ${\allleadsto}(i, a_e)$ represent $i$ being given an explanation about the psychological phenomenon described in the quote above.
  Let ${\allleadsto}(i, a_e)$ represent $i$ being given the following argument. “When tested, $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly; whereas $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly. It follows than $m_1$ answers on average less well than $m_2$. Observing the candidates take the tests may yield a contrary impression; this is a well-known psychological phenomenon depending on the order of the questions that the candidates answer correctly.”
  Let $\prop_1$ represent the choice of $m_1$ and $\prop_2$ that of $m_2$.

  If the prediction described in the quote applies to $i$, the relation $\ileadsto$ is as follows, $\forall k \in \N^*$ (recall that for $\args \subseteq \allargs$, $\args^k$ represents the set of sequences of length $k$ using arguments from $\args$): $\forall \hist \in \set{a_e}^k, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_1, a_2}^k, \hist \ileadsto \prop_1$; $\forall \hist \in \set{a_1, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_2, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \allargs^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$. The values of ${\allleadsto}(i, \hist)$ for $\hist = \emptyset$ and for $\hist \in \allargs^k \suchthat a_e \notin \histend$ are undetermined by the prediction, but whatever they are, $a_e$ is a decisive argument for $\prop_2$, hence, $i$’s deliberated choice is $\prop_2$.
\end{example}

@@

\subsection{Claims and observable basis}
% Such a deduction should use, as much as possible, the observational basis, that is, the propositions of the form $\alpha \ileadsto p$ that can be obtained experimentally.
Note first that given a relation ${\allleadstog} \in \allleadstos$, $\powerset{\allleadstog}$ denotes the set of relations over $(I × \allhists) × P$ that refine $\allleadstog$ (thus, each element $f \in \powerset{\allleadstog}$ is right-unique but non necessarily total, meaning that it does not necessarily cover $(I × \allhists)$).

@@

Given a pair $(I, \allargs)$, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhists) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
The set $\Theta$ contains the a priori possible observations, that is, those that can be considered possible when nothing is known about $\allleadsto$.
We say that an observation $\theta$ is compatible with a claim $C$ iff
$\theta \in C^\subseteq$, equivalently, iff
$\theta \in \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$.
Thus, given ${\allleadstog} \in \allleadstos$, the set $\Theta \cap \powerset{\allleadstog}$ is the set of observations compatible with ${\allleadstog}$.

Given an observation $\theta$, let $\theta^{-1}(P) \subseteq I × \allhists$ denote the pairs $(i, \hist)$ in $\theta$.
Let $\incr(\allhists) = \set{\emptyset} \cup \cup_{\emptyset \neq N \subseteq \N} \set{A(N) \suchthat A \in (\allhists)^N \land [\card{A_i} = i] \land [i < j \implies A_i \subsetneq A_j]} \subseteq \powerset{\allhists}$ denote the possibly empty embedded sequences of paths.
\commentOC{TODO define $\incr(\allhists) = \set{H \wsub \allhists \suchthat \card(H) ≤ \card(H') \implies H \wsub H'}$.}
An element $\theta^{-1}(P)$ can also be seen as a (finite) function associating to each $i \in I$ an element of $\incr(\allhists)$.
Therefore, we let $\finite(\incr(\allhists)^I) = \set{\theta^{-1}(P) \suchthat \theta \in \Theta}$ denote the set of possible observations restricted to $I × \allhists$, the elements of which being called \emph{a priori observation}, where $\finite(\incr(\allhists)^I)$ denote the functions $f: I \mapsto \incr(\allhists)$ with finite support, thus $\card{f^{-1}(\incr(\allhists) \setminus \emptyset)} < \N$.
Note that $\allpriobss$ and $\incr(\allhists)^I$ are downwards closed, meaning that $\forall O \in \allpriobss: O' \subseteq O \implies O' \in \allpriobss$ and $\forall O \in \incr(\allhists)^I: O' \subseteq O \implies O' \in \incr(\allhists)^I$.
Let also $\max\incr(\allhists) = \set{A \in \incr(\allhists) \suchthat \nexists A' \in \incr(\allhists) \suchthat A \subset A'} = \set{A \in \incr(\allhists) \cap (\allhists)^\N}$ denote the maximal elements of $\incr(\allhists)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\N$.

Let the \emph{simple a priori observations} be defined as $\cup_{J \subseteq_\finite I} (\allhists)^J$, equivalently, as the right-unique finite relations over $I × \allhists$.
Given a simple a priori observation $O: J \mapsto \allhists$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhists \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.

Similarly, we can view an observation $\theta$ as a function $\theta: I \mapsto \cup_{A \in \incr(\allhists)} P^A$ and thus $\Theta = \finite((\cup_{A \in \incr(\allhists)} P^A)^I)$, where $\finite$ designates the finite relations (considered as a set of triples).
Note that $(\cup_{A \in \max \incr(\allhists)}P^A)^I$ is the set of functions that associate to each $I$ a maximal increasing sequence of paths, together with values from $P$.

Given a claim $C$, we can also define the set $\Theta \cap C^\subseteq$ of possibilities for increasing sequences corresponding to the claim.
This set is downwards-closed, as both $\Theta$ and $C^\subseteq$ are.

@@

At our disposal is the procedure of empirical rejection, that consists in directly invalidating a claim by observing something that contradicts it.
\begin{definition}
  Given an exposure protocol $\allleadsto$, we say that $C$ is \emph{rejectable} iff
  $\Theta \cap \powerset{\allleadsto} \nsubseteq C^\wsub$.
\end{definition}

@@

\Cref{def:falsw} fills the gap to obtain that $C$ holds iff it is not rejectable.
The property demands that whatever the attitude of individuals, if the attitude is not compatible with the claim, then it is possible to observe that it is not.
\begin{definition}
  \label{def:falsw}
  A claim $C$ is \emph{falsifiable or trivial} iff
  $\forall {\allleadstog} \notin C: \Theta \cap \powerset{\allleadstog} \nsubseteq C^\wsub$.
\end{definition}

@@

\Cref{th:holdsiff} shows that falsifiability indeed fills that gap:
falsifiability guarantees that a claim holds if, and only if, it is not rejectable.
\begin{theorem}
  \label{th:holdsiff}
  For any falsifiable or trivial claim $C$: $C \ni {\allleadsto}$ iff $\Theta \cap \powerset{\allleadsto} \wsub C^\wsub$.
\end{theorem}
\begin{proof}
  Consider any falsifiable $C$.
  Using the contrapositive of \cref{def:fals}, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
  In particular,
  $\nexists θ \in \Theta \cap \powerset{\allleadsto} \suchthat \theta \notin C^\wsub \implies {\allleadsto} \in C$.
  The reverse implication is proven by \cref{th:ex-post}.
\end{proof}

\begin{definition}
  A claim is \emph{strongly unfalsifiable} iff
  $\Theta \wsub C^\wsub$.
\end{definition}
\Cref{ex:disjR,ex:bigor} illustrate, as well as \cref{ex:existsParticular} when $I$ is infinite.
\begin{definition}
  A claim is \emph{strictly unfalsifiable} iff
  it is unfalsifiable and not strongly unfalsifiable.
\end{definition}

Making a strongly unfalsifiable claim more precise ($C = (C_1 \cap C_2) \sub C_1$ in \cref{th:strongUToStrictU}) can make it strictly unfalsifiable.
Also, a strictly unfalsifiable claim can be made falsifiable by picking a single relation from the claim.

But, it does not hold that more precise claims are always more falsifiable:
making a falsifiable claim more precise ($C = (C_1 \cap C_2) \sub C_2$ in \cref{ex:partlyU}) can make it strictly unfalsifiable.
(In fact, \cref{ex:partlyU} shows that the relation is not one-way: going from a strongly unfalsifiable ($C_1$), or from a falsifiable ($C_2$), claim, to a more precise one ($C = C_1 \cap C_2$) yields a strictly unfalsifiable claim.)

\begin{example}
  \label{ex:allParticular}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}

The following procedure permits to determine whether a claim is falsifiable.
Given a set of observations $S \wsub \Theta$, define the relations that are observation-compatible with $S$ as $E(S) = \set{{\allleadstog} \in \allleadstos \suchthat \forall \theta \in \Theta: {\allleadstog} \cap \theta \in S}$.
Given a claim $C$, define the set of its observation-compatible relations as $E(C) = E(C^\wsub \cap \Theta)$ (reusing the letter $E$ by abuse of notation).
Note that this set extends $C$, in the sense that $C \wsub E(C)$.
The claim $C$ is falsifiable iff it is closed under extension to observation-compatible relations, that is, iff $E(C) \subseteq C$.
\begin{theorem}
  \label{thm:caractFals}
  A claim $C$ is falsifiable or trivial iff $E(C) \wsub C$, or equivalently, iff 
  $\forall {\allleadstog} \in \allleadstos$:
  \[\set{\restr{\allleadstog}{O} \suchthat O \in \allpriobss} \subseteq C^\subseteq \implies {\allleadstog} \in C.\]
\end{theorem}
\begin{proof}
  Note that
  $E(C) = E(C^\wsub \cap \Theta) = \set{{\allleadstog} \in \allleadstos \suchthat \forall O \in \allpriobss: \restr{\allleadstog}{O} \in C^\wsub}$.

Define the \emph{suffix} relation $R = \set{(\hist, \histp) \in \allhists × \allhists \suchthat \histp = (\hist, .)}$ as the (infinite) tree whose set of nodes is $\allhists$ and which links  argumentative paths to all of their direct suffixes.
Note that a path in such a tree (an increasing sequence of elements in $\allhists$) corresponds to an argumentative path, that is, to an element of $\allhists$.

Given an attitude $\allleadsto$, deliberated choices are represented by an element $\pi({\allleadsto}) \subseteq I × P$ (thus with $\pi({\allleadsto})(i) = P_i$) which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadsto})(i)} ≤ 1$).
Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadsto}) \in (P \cup \set{\emptyset})^I$.

A claim $C$ is \emph{informative} iff $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
A claim $C$ is \emph{informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) ≠ P \cup \set{\emptyset}$.
A claim $C$ is \emph{strongly informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) \ssub P$.
% A claim $C$ is \emph{indicative} iff $\exists H \in \finite(\incr(\allhists)), i \in I \suchthat \pi(\set{{\allleadstog} \suchthat H \wsub \ileadstoinvg(P)} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
A claim $C$ is \emph{indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub \suchthat \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
\begin{remark}
  Informativeness permits mere counting: the claim that exactly two persons deliberately believe $\phi$ is informative.
  Informativeness may be a desirable property (rather than informativeness beyond counting) as one may want to know whether a given proposition is believed by a majority of individuals, or whether a given proposition is believed by nobody.
  Note also that strong informativeness beyond counting implies informativeness beyond counting and indicativeness.
  Note also that informativeness beyond counting implies informativeness.
\end{remark}
\begin{remark}
  We could weaken indicativeness by allowing for disjuncts: observing either that $\hist \ileadsto \phi$ or that $\hist \ileadsto \psi$ permits to deduce something about $P_i$.
  (Or more complex formulas under the form of a set of possible functions in $P^H$?)
  (Actually I am not sure that this really weakens the condition.)
\end{remark}

@@

We are now interested in the interplay between properties of holding, anonymity, (strong) informativeness beyond counting, and falsifiability.
\Cref{th:hsif,th:hif,th:asif} show their compatibility when one of holding or anonymity is not required (except that informativeness beyond counting cannot be made strong in the edge case where $\forall i \in I: P_i = \emptyset$).

@@

\begin{example}[To be completed]
  Assume that $\exists \ar_j ≠ \ar_k, J, K \subset I \suchthat J \cup K = I \land \card{J} \notin \N \land \card{K} \notin \N \land \forall j \in J: \ar_j \ileadstost[j] \phi \land \forall k \in K: \ar_k \ileadstost[k] \phi \land \forall \ar \in \allargs \setminus \set{\ar_j, \ar_k}, i \in I: \ar \nileadstost \phi$.
  Then no suitable $C$ exists?

@@

  To define this formally, note that either $\arga$ is a decisive argument for $\pga$, or some paths challenge this claim, namely those $\hist \in \allhists$ such that $[\arga \in \histend \land \hist \nileadsto \pga]$.
  Generalizing this observation, given $i \in I$, define $\dgi(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \in \histend \land \hist \nileadsto \pga} \subseteq \dg(\ar)$ as the subset of defenders of $\ar$ required for convincing $i$ of choosing $\pga$.
  Define $\gargsi \subseteq \allargs$ as the transitive closure of $\arga$ under $\dgi$: $\gargsi = \cup_{k \in \N} (\dgi)^k(\arga)$. The set $\gargsi$ is the set of arguments required to convince $i$ of choosing $\pga$.

>>>>

While $I$ and $\allargs$ are fundamental sets whose elements are considered elementary, a few notations and concepts are required to define ${\allleadsto}$.
Throughout the article, $\Z$ designates the integers (including $0$) and $\Zp = \Z \setminus \set{0}$ designates the positive numbers.
Given $j, l \in \Z$, the notation $\intvl{j, l}$ represents $\set{k \in \Z \suchthat j ≤ k ≤ l}$ (thus $\forall j \in \Zp: \intvl{j, 0} = \emptyset$).
Define $\allhists = \bigcup_{k \in \Z} \allargs^{\intvl{1, k}}$ as the finite sequences of arguments, including the empty sequence.
A generic element of $\allhists$ (a possibly empty finite sequence of arguments) is denoted by $\hist$ and called an argumentative path, or simply a path. Its length is denoted by $\card{\hist} \in \Z$ and its elements, $\hist(k)$ or $\hist_k$.
Thus, given an argumentative path $\hist \in \allhists$, $\forall k \in \intvl{1, \card{\hist}}: \hist(k) = \hist_k \in \allargs$, and $\hist = \emptyset ⇔ \card{\hist} = 0$. A path $\hist \in \allhists$ is a prefix of a path $\histp \in \allhists$ whenever $\hist \subseteq \histp$, thus, $\forall k \in \intvl{1, \card{\hist}}: \hist_k = \histp_k$.
Given any $\hist \in \allhists$, $\intvl{\hist} = \set{\restr{\hist}{\intvl{1, k}} \suchthat k \in \intvl{0, \card{\hist}}}$ denotes the set of prefixes of $\hist$.

@@

Given an behavior function $\allleadstog$, deliberated choices are represented by an element $\pi({\allleadstog}) \subseteq I × P$ (thus with $\pi({\allleadsto})(i) = P_i$) which is right unique (meaning that $\forall i \in I: \card{\pi({\allleadstog})(i)} ≤ 1$).
Equivalently, let $(P \cup \set{\emptyset})^I$ denote the right unique relations over $I × P$; and then the deliberated choices are an element $\pi({\allleadstog}) \in (P \cup \set{\emptyset})^I$.

\subsection{An example and a discussion about observability}
The following toy example is inspired by the following argument from \citet[p.~59]{railton_facts_2003}.
\begin{quote}
  An experiment in cognitive psychology reveals that when subjects observe two individuals taking a test, one of whom answers a high percentage of the early questions correctly but then falters, while the other does
  poorly initially but then answers a high percentage of the later questions
  correctly, the first is usually viewed as more able, even though in the end
  each answers the same number of questions correctly in all. If the subjects had been asked which test-taker they would prefer as a math tutor,
  they likely would have answered “The first,” and perhaps they would also
  have been willing to pay a premium to secure his services. But if they
  were to become convinced of the influence of sheer order on their evaluations of relative ability, they presumably would no longer want their
  initial preference for the first test-taker to influence their choices – or
  willingness to pay – in this way.
\end{quote}
\begin{example}[Math tutor]
  \label{ex:tutor}
  Let $I$ be a set of individuals desiring to evaluate two candidates $\set{m_1, m_2}$ for math tutoring.
  Consider one individual $i \in I$.
  Let ${\allleadsto}(i, a_1)$ represent $i$ being shown a test of candidate $m_1$ wherein $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly.
  Let ${\allleadsto}(i, a_2)$ represent $i$ being shown a test of candidate $m_2$ wherein $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly.
  %	Let ${\allleadsto}(i, a_e)$ represent $i$ being given an explanation about the psychological phenomenon described in the quote above.
  Let ${\allleadsto}(i, a_e)$ represent $i$ being given the following argument. “When tested, $m_1$ answers 70\% of the first half of questions correctly but then only 40\% of the other half correctly; whereas $m_2$ answers 45\% of the first half of questions correctly, then 75\% of the other half correctly. It follows than $m_1$ answers on average less well than $m_2$. Observing the candidates take the tests may yield a contrary impression; this is a well-known psychological phenomenon depending on the order of the questions that the candidates answer correctly.”
  Let $\prop_1$ represent the choice of $m_1$ and $\prop_2$ that of $m_2$.

  If the prediction described in the quote applies to $i$, the relation $\ileadsto$ is as follows, $\forall k \in \Zp$ (recall that for $\args \subseteq \allargs$, $\args^k$ represents the set of sequences of length $k$ using arguments from $\args$): $\forall \hist \in \set{a_e}^k, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_1, a_2}^k, \hist \ileadsto \prop_1$; $\forall \hist \in \set{a_1, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \set{a_2, a_e}^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$; $\forall \hist \in \allargs^k \suchthat a_e \in \histend, \hist \ileadsto \prop_2$. The values of ${\allleadsto}(i, \hist)$ for $\hist = \emptyset$ and for $\hist \in \allargs^k \suchthat a_e \notin \histend$ are undetermined by the prediction, but whatever they are, $a_e$ is a decisive argument for $\prop_2$, hence, $i$’s deliberated choice is $\prop_2$.
\end{example}

@@

\subsection{Claims and observable basis}
% Such a deduction should use, as much as possible, the observational basis, that is, the propositions of the form $\alpha \ileadsto p$ that can be obtained experimentally.
Note first that given a relation ${\allleadstog} \in \allleadstos$, $\powerset{\allleadstog}$ denotes the set of relations over $(I × \allhists) × P$ that refine $\allleadstog$ (thus, each element $f \in \powerset{\allleadstog}$ is right-unique but non necessarily total, meaning that it does not necessarily cover $I × \allhists$).

@@

Define the increasing sets of paths as the set $\incr(\allhists) = \set{H \fsub \allhists \suchthat \card(H) ≤ \card(H') \implies H \wsub H'} \wsub \powerset{\allhists}$. A set of paths $H \in \incr(\allhists)$ can be strictly ordered by the lengths of the paths in $H$ and can thus also be considered as a sequence of paths.
Note that $\incr(\allhists)$ includes both the empty set of paths $\emptyset$ and the set of paths $\set{\emptyset}$ containing only the empty path.
A non empty set of paths $H \in \incr(\allhists)$ has a unique maximal element $\set{\max H} = \set{\hist \in H \suchthat \forall \histp \in H: \histp \wsub \hist}$.
A non empty set of paths $H \in \incr(\allhists)$ contains all its prefixes (meaning, $\forall \hist \in H: \set{\histp \wsub \hist} \wsub H$) iff $H = \intvl{\max H}$.
Let $\finite(\incr(\allhists)^I)$ denote the functions $f: I \mapsto \incr(\allhists)$ with finite support, thus, satisfying $\card{f^{-1}(\incr(\allhists) \setminus \emptyset)} \in \N$.
An element $Q \in \allpriobss$ \commentOC{previously denoted $O$ and called a priori observation} is called a query.
\commentOC[Note that $\incr(\allhists)^I$ and $\allpriobss$ are downwards closed, meaning that $\forall O \in \incr(\allhists)^I: \set{O' \subseteq O} \wsub \incr(\allhists)^I$ and $\forall O \in \allpriobss: \set{O' \subseteq O} \wsub \allpriobss$.]{To be deleted.}

An observation associates to a query an element of $P$ per queried element, thus, the set of possible observations is $\Theta = \cup_{Q \in \allpriobss} P^Q$.
In other words, an observation $θ \in \Theta$ is a right unique finite subset of $(I × \allhists) × P$ such that $\forall i \in I, (i, \hist, p), (i, \histp, q) \in θ: \card{\hist} ≤ \card{\hist'} \implies \hist \subseteq \hist'$.
Given an observation $\theta$, let $\theta^{-1}(P) \in \allpriobss$ denote the queried elements in $\theta$, which can also be considered as $\theta^{-1}(P) \subseteq I × \allhists$, the pairs $(i, \hist)$ in $\theta$.
Similarly, we can view an observation $\theta$ as a function $\theta: I \mapsto \cup_{H \in \incr(\allhists)} P^H$ and thus $\Theta = \finite((\cup_{H \in \incr(\allhists)} P^H)^I)$, where $\finite$ designates the finite relations (considered as a set of triples).
\commentOC[Note that $(\cup_{H \in \max \incr(\allhists)}P^H)^I$ is the set of functions that associate to each $I$ a maximal increasing sequence of paths, together with values from $P$.]{To be deleted.}

\commentOC[Let also $\max\incr(\allhists) = \set{A \in \incr(\allhists) \suchthat \nexists A' \in \incr(\allhists) \suchthat A \subset A'}$ being equal to $\set{A \in \incr(\allhists) \cap (\allhists)^\Z}$ denote the maximal elements of $\incr(\allhists)$, in the sense of containing sequences that are not a subsequence of another sequence; equivalently, containing those sequences whose sequence of cardinals of their elements equals $\Z$.]{To be deleted.}

We say that an observation $\theta$ is compatible with a behavior ${\allleadstog} \in \allleadstos$ iff $\theta \subseteq \powerset{\allleadstog}$, that is, $\forall (i, \hist, p) \in \theta: (i, \hist, p) \in \powerset{\allleadstog}$.
Thus, given ${\allleadstog} \in \allleadstos$, the set $\Theta \cap \powerset{\allleadstog}$ is the set of observations compatible with ${\allleadstog}$.
Similarly, an observation $\theta$ is compatible with a claim $C$ iff
$\theta \in \cup_{{\allleadstog} \in C} \powerset{\allleadstog}$, equivalently, iff
$\theta \in C^\subseteq$.
The set $\Theta \cap C^\subseteq$ is the set of observations compatible with the claim.
This set is downwards-closed, as both $\Theta$ and $C^\subseteq$ are.

\commentOC[Let the \emph{simple a priori observations} be defined as $\cup_{J \subseteq_\finite I} (\allhists)^J$, equivalently, as the right-unique finite relations over $I × \allhists$.
  Given a simple a priori observation $O: J \mapsto \allhists$, we can define the a priori observation $O_O = \set{(i, \hist) \in J × \allhists \suchthat \forall i \in J: \hist \subseteq O(i)}$ as the completion of $O$ to all sub-paths in $O$.]{To be deleted.}

It is important to realize that $\Theta$ is the set of \emph{a priori} possible observations, meaning, those that are conceivable, possibly counter-factually. The set of observations that can result from actually observing the behavior ${\allleadsto}$ is 
$\Theta \cap \powerset{\allleadsto} = \set*{\restr{{\allleadsto}}{Q} \suchthat Q \in \allpriobss}$.

@@

At our disposal is the procedure of empirical rejection, that consists in directly invalidating a claim by observing something that contradicts it.
\begin{definition}
  Given a behavior $\allleadsto$, we say that $C$ is \emph{rejectable} iff
  $\Theta \cap \powerset{\allleadsto} \nsubseteq C^\wsub$.
\end{definition}

@@

\Cref{def:fals} fills the gap by defining a condition that ensures that $C$ holds iff it is not rejectable.
The property demands that whatever the behavior of individuals, if their behavior is not compatible with the claim, then it is possible to observe that it is not.
\begin{definition}
  \label{def:fals}
  A claim $C$ is \emph{falsifiable} iff $C \neq {\allleadstos} \land
  \forall {\allleadstog} \notin C: \Theta \cap \powerset{\allleadstog} \nsubseteq C^\wsub$.
\end{definition}

@@

\Cref{th:holdsiff} shows that falsifiability indeed fills that gap:
falsifiability guarantees that a claim holds if, and only if, it is not rejectable.
\begin{theorem}
  \label{th:holdsiff}
  For any falsifiable or trivial claim $C$: $C \ni {\allleadsto}$ iff $\Theta \cap \powerset{\allleadsto} \wsub C^\wsub$.
\end{theorem}
\begin{proof}
  Consider any falsifiable claim $C$, thus, 
  $\forall {\allleadstog} \notin C: \exists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub$.
  Using the contrapositive, $\forall {\allleadstog} \in \allleadstos: \nexists θ \in \Theta \cap \powerset{\allleadstog} \suchthat \theta \notin C^\wsub \implies {\allleadstog} \in C$.
  In particular,
  $\nexists θ \in \Theta \cap \powerset{\allleadsto} \suchthat \theta \notin C^\wsub \implies {\allleadsto} \in C$.
  The reverse implication is proven by \cref{th:ex-post}.
\end{proof}

\begin{example}
  \label{ex:allParticular}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable:
  given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}

\begin{remark}
  Making a claim more precise (meaning going from a claim $C$ to $C' \ssub C$) can make it falsifiable, or conversely, can make it unfalsifiable.
  Given $\hist, i$, consider the claim $C_2 = \hist \ileadstog \phi$. It is falsifiable.
  Now consider the claim $C = C_1 \cap C_2$ with $C_1$ being the claim “every individual chooses $\phi$ after seeing solely either $\ar$ or $\ar'$”. It is more precise but unfalsifiable.
 But we can make it falsifiable again by making it even more precise (picking any single relation).
 (See \cref{rq:precise}.)
\end{remark}

\subsection{More properties}
A claim $C$ is \emph{informative} iff $\pi(C) = \set{\pi(\allleadstog) \suchthat {\allleadstog} \in C} ≠ (P \cup \set{\emptyset})^I$.
A claim $C$ is \emph{informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) ≠ P \cup \set{\emptyset}$.
A claim $C$ is \emph{strongly informative beyond counting} iff $\exists i \in I \suchthat \pi(C)(i) \ssub P$.
% A claim $C$ is \emph{indicative} iff $\exists H \in \finite(\incr(\allhists)), i \in I \suchthat \pi(\set{{\allleadstog} \suchthat H \wsub \ileadstoinvg(P)} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
A claim $C$ is \emph{indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$ compatible with any (possibly counter-factual) world in $C$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.
A claim $C$ is \emph{truly indicative} iff $\exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadsto} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
A claim $C$ is \emph{newly indicative} iff $\forall {\allleadstog} \in C: \exists i \in I, \theta \in \Theta \cap (\allhists × \set{i} × P) \wsub {\allleadstog} \suchthat \emptyset ≠ \pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$. Indicativity mandates that when knowing a finite number of observations about a given $i$ compatible with any (possibly counter-factual) world in $C$, $C$ permits to deduce something (different than $\emptyset$) about $P_i$.

\begin{remark}
  Informativeness permits mere counting: the claim that exactly two persons deliberately believe $\phi$ is informative.
  Informativeness may be a desirable property (rather than informativeness beyond counting) as one may, for example, want to know whether a given proposition is believed by a majority of individuals.
  Note also that strong informativeness beyond counting implies informativeness beyond counting and indicativeness; and
  that informativeness beyond counting implies informativeness.
\end{remark}

@@

\Cref{th:AHFimpl} and related show that anonymous and falsifiable claims that hold exist iff the situation does not satisfy $\forall \hist: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$.

Let us determine which situations admit anonymous and falsifiable claims that hold and are indicative (or other?).

@@

\begin{example}[To be completed]
  Assume that $\exists \ar_j ≠ \ar_k, J, K \subset I \suchthat J \cup K = I \land \card{J} \notin \Z \land \card{K} \notin \Z \land \forall j \in J: \ar_j \ileadstost[j] \phi \land \forall k \in K: \ar_k \ileadstost[k] \phi \land \forall \ar \in \allargs \setminus \set{\ar_j, \ar_k}, i \in I: \ar \nileadstost \phi$.
  Then no suitable $C$ exists?

@@

  To define this formally, note that either $\arga$ is a decisive argument for $\pga$, or some paths challenge this claim, namely those $\hist \in \allhists$ such that $[\arga \in \histend \land \hist \nileadsto \pga]$.
  Generalizing this observation, given $i \in I$, define $\dgi(\ar) = \set{\dg(\ar, \hist) \suchthat \ar \in \histend \land \hist \nileadsto \pga} \subseteq \dg(\ar)$ as the subset of defenders of $\ar$ required for convincing $i$ of choosing $\pga$.
  Define $\gargsi \subseteq \allargs$ as the transitive closure of $\arga$ under $\dgi$: $\gargsi = \cup_{k \in \Z} (\dgi)^k(\arga)$. The set $\gargsi$ is the set of arguments required to convince $i$ of choosing $\pga$.
